---
title: "Sentiment Analysis"
author: "Yasin Khadem Charvadeh"
output:
  html_document:
    df_print: paged
    code_folding: "show"
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      tidy = TRUE)
```

For data request please email me at <ykhademc@uwo.ca>.

```{r}
library(kableExtra)
library(stringr)
library(wordcloud)
library(SentimentAnalysis)
library(SnowballC)
library(RSentiment)
library(textclean)
library(tm)
library(textstem)
library(tidyverse)
library(syuzhet)
## import the the data set

podcast_data <- read_csv("~/podcast_data_unlabelled_test.csv")

```
#### find the unique Podcasts
```{r}
uni_podcast_data <- podcast_data[!duplicated(podcast_data$title),]

uni_podcast_data %>% kbl(align = rep("c", 9), escape = TRUE, longtable = TRUE) %>%
    kable_styling(bootstrap_options = c("basic", "hover"), fixed_thead = TRUE) %>%
    column_spec(2, color = "green") %>% 
    scroll_box(width = "1050px", height = "300px")
```

Cleaning text data may vary depending on the nature of the text. You may need to explore the text first and then decide about appropriate manipulation.
```{r}
## Make sure there is space after comma

text_data <- add_comma_space(uni_podcast_data$summary)

## Remove URL

text_data <- replace_url(text_data)

## Remove punctuation and replace it with space

text_data <- gsub(pattern = "\\W", replacement = " ", text_data)

## Remove numbers and replace with space

text_data <- gsub(pattern = "\\d", replacement = " ", text_data)

## Convert all the text into lower case

text_data <- tolower(text_data)

## Replace symbols

text_data <- replace_symbol(text_data)

## Remove stop words

text_data <- removeWords(text_data, stopwords("english"))

## Remove single characters

text_data <- gsub(pattern = "\\b[A-z]\\b{1}", replacement = " ", text_data)

## Remove extra white spaces

text_data <- stripWhitespace(text_data)

## Replace Word Elongations

text_data <- replace_word_elongation(text_data, impart.meaning = TRUE)

## Remove non-english charaters

for (i in 1:length(text_data)){
  text_data[[i]] <- gsub('[^a-zA-Z|[:blank:]]', "", text_data[[i]])
}
```


The R code below uses the analyzeSentiment() function to compute sentiment statistics for each podcast.

```{r}

## Matrix with sentiment values

Sent_score <- analyzeSentiment(text_data, language="english", stemming = FALSE, removeStopwords = FALSE)
Sent_score[1:4,]
```

```{r}

## Obtain sentiment scores of different emotions

EMO <- get_nrc_sentiment(text_data)

EMO_plot <- rownames_to_column(as.data.frame(colSums(EMO)))

colnames(EMO_plot) <- c("emotion", "count")

## Make a barplot of the emotions

EMO_plot %>% ggplot() +
  geom_bar(aes(x = reorder(emotion, count), y = count, fill = count), 
  stat = "identity") + scale_fill_viridis_c() +
  labs(x = "Emotion", y = "Total count") +
  ggtitle("Emotions of Podcast summaries") +
  theme(plot.title = element_text(hjust=0.5), 
  axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r}

## Load the text data as a Corpus

corpus <- iconv(text_data)
corpus <- Corpus(VectorSource(corpus))
inspect(corpus[1:5])

## construct a document matrix that contains the frequency of words

doc_m <- TermDocumentMatrix(corpus)
doc_m <- as.matrix(doc_m)
doc_m[1:10, 1:10]
```
To show the most frequent words, we perform a text analysis using word clouds which visualize word frequencies by using diﬀerent sizes of words.

```{r}

word <- sort(rowSums(doc_m), decreasing = TRUE)
wordcloud(words = names(word),
          freq = word,
          min.freq=5,
          max.words = 1000,
          random.order = FALSE,
          scale = c(4, 0.5),
          colors = rainbow(10))
```

```{r}

## Make a barplot for emotions of podcast summaries by rating

Rating_high <- rownames_to_column(as.data.frame(colSums(EMO[which(uni_podcast_data$rating_value>=4.7),])))

colnames(Rating_high) <- c("emotion", "count")

Rating_high %>% ggplot() +
  geom_bar(aes(x = reorder(emotion, count), y = count, fill = count), 
  stat = "identity") + scale_fill_viridis_c() +
  labs(x = "Emotion", y = "Total count") +
  ggtitle("Emotions of top-rated Podcast summaries") +
  theme(plot.title = element_text(hjust=0.5), 
  axis.text.x = element_text(angle = 45, hjust = 1))


Rating_low <- rownames_to_column(as.data.frame(colSums(EMO[which(uni_podcast_data$rating_value<4.7),])))
colnames(Rating_low) <- c("emotion", "count")


Rating_low %>% ggplot() +
  geom_bar(aes(x = reorder(emotion, count), y = count, fill = count), 
  stat = "identity") + scale_fill_viridis_c() +
  labs(x = "Emotion", y = "Total count") +
  ggtitle("Emotions of low-rated Podcast summaries") +
  theme(plot.title = element_text(hjust=0.5), 
  axis.text.x = element_text(angle = 45, hjust = 1))
```
